On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-11-24 paper.tex
Bibliography
I have just added bibliography file and solve the citation in the paper.

In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{RNAorigami} the co-transcriptional folding of RNA is controlled by careful design of the DNA template. As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands. 
Geary et al.~\cite{Oritatami} proposed a mathematical model for this process, called oritatami system.
It has been shown~\cite{Simulator} that the model is computationally universal by simulating cyclic tag systems introduced by Cook~\cite{Cook110}. 
The simulation involves a very large and complex oritatami system. 
One future direction of research is to find smaller universal oritatami system.

@@

\section{Problem description}

In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.

@@

>>>>

In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{GearyRothemundAndersen2014} the co-transcriptional folding of RNA is controlled by careful design of the DNA template. As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands. 
Geary et al.~\cite{GeMeScSe2016} proposed a mathematical model for this process, called oritatami system.
It has been just shown in \cite{GeMeScSe2018} that the model is efficiently Turing universal by simulating cyclic tag systems introduced by Cook~\cite{Cook2004}. 
The simulation involves a very large and complex oritatami system. 
One future direction of research is to find smaller universal oritatami system.

@@

%-------------------------------------------------------
	\section{Problem description}
%-------------------------------------------------------

In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.

@@

\bibliographystyle{splncs03}
\bibliography{tamc2019.bib}
